--- 
title: "Computational Social Science at Scale"
author: "Stefan Wojcik"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/comp-nuggets
description: "This is a book about computational social science for early-career researchers, journalists, nonprofitteers, and graduate students in computational social science programs."
---

# Prerequisites {#prereqs}

You don't need to be a math or science nerd to code. Like anything, you just need practice. You will benefit from a background in Statistics or Computer Science to deeply understand this book, but it is not a requirement. You will get a lot out of this book without them. 

I grew to understand the power of programming to deconstruct an increasingly digital world. Web sites like Google, Facebook, and Twitter provide incredible real-time access to information that aid us in understanding changes in society. But they don't really make that data available easily - at least not in large quantities. It's frankly hard to bulk download data from most web sites. In some cases it's also illegal or unethical, so just keep that in mind :). 

## Not a Drop to Drink

Data are literally everywhere, but they are usually not made for you to collect or understand. 

This book is about making data more accessible to you. You may be interested in writing a program to systematically download certain tables from a web site because they tell you something about the results of a sports game or election. Or you may be interested in all of the text on specific web pages because they tell you something about how people talk to each other. 

That is why you need to learn to code. 

## Flavors of Data Science 

Not all data science is the same, and for good reason. Huge variation is what it means to be a data scientist. 

## Who this book is for

Key audiences for this book.  

## Book overview

I wrote this book 

## Motivating Example: Trusting the News

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
