--- 
title: "Computational Nuggets"
author: "Stefan Wojcik"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/comp-nuggets
description: "This is a book about computational social science for journalists, nonprofit researchers, or graduate students in recently-turned-quantitative social science programs."
---

# Prerequisites {#prereqs}

I am, by all accounts, an unlikely evangelist for Data Science. I wasn't a math nerd in high school or college, nor did I have any idea how to code. I was much more interested in Social Sciences, specifically Political Science. 

But I grew to understand the power of code to probe an increasingly digital world. While web sites like Google, Facebook, and Twitter provide incredible real-time access to information that aid us in understanding changes in society, they don't really make that data available at scale. Unless you're already a programmer and have special access, it's hard to bulk download data from the most popular web sites. 

## Not a Drop to Drink

Data are almost literally everywhere, but they are usually not made for you to collect or understand. 

That is why you need to learn to code. 

## Flavors of Data Science 

Not all data science is the same, and for good reason. Huge variation in what it means to be a data scientist. 

## Who this book is for

Key audiences for this book.  

## Book overview

I wrote this book 

## Motivating Example: Trusting the News

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
